Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-22 response/response.tex

% Reviewer 1: Q1
\begin{review}
The text (including the abstract) contains many typographical and grammatical errors, which are distracting and render the manuscript difficult to read.
The authors should proofread the document carefully.
\end{review}

\begin{response}
\todo{Proofread by everyone}
\end{response}

% Reviewer 1: Q2
\begin{review}
In the introduction, four example applications are mentioned for which the dataset can be used.
According to the title of the paper the dataset is proposed for phenotyping applications.
Thus, the authors should elaborate on why and how the computer vision tasks they mention are relevant to plant phenotyping.
The authors should also include few key references to works that use (or discuss) such features for plant phenotyping.
\end{review}

\begin{response}
We have added two paragraphs with related references to better connect plant phenotyping and computer vision tasks. 
Please refer to paragraph $2$ and $3$ in Sec. $1$. 
\end{response}

% Reviewer 1: Q3
\begin{review}
The authors should clarify what is intended by ``leaf alignment" and why it is important, since this feature is probably less common in plant phenotyping applications than the others that are mentioned.
\end{review}

\begin{response}
Leaf alignment aims to estimate the structure of a leaf.
In the case where the leaf structure is simple (e.g., ellipsoid-shaped leaf), leaf alignment amounts to estimating the inner and outer tips of the leaf.
For more complex leaf structure (e.g., maple leaf), leaf alignment will estimate additional landmarks on the leaf contour that will consistently appear in all leaves.
Leaf alignment is important for two reasons:
First, it goes beyond leaf segmentation and provides structural information of a leaf - a discriminative signature for a leaf.
For example, ~\cite{cerutti2013understanding} uses a polygonal leaf model for leaf segmentation and plant identification.
Second, plant biologists often hypothesize that different local parts of a leaf may have different photosynthetic efficiency.
This leaf structure information can be used to quantitatively study this hypothesis and its implication to the overall photosynthetic efficiency of a plant.
\end{response}

@@

% Reviewer 1: Q4
\begin{review}
Since multi-modality is a strength of the proposed dataset, the authors should motivate better their choice of imaging modalities (i.e. fluorescence, infrared, RGB color, and depth), highlighting their importance and what information they convey on plant structure and functions.
Apparently, this is only partly done for depth at the end of Sec. $2$.
\end{review}

\begin{response}
We have inserted a brief explanation with references in the last paragraph of Sec. $2$. 
\end{response}

% Reviewer 1: Q5
\begin{review}
Figure $1$ should be augmented (or a separate figure should be created) with zoom in details showing how the same plant parts (or scene portions) appear in different modalities.
This would help the reader get a better idea of the contrast and the type of information conveyed by each of the modalities adopted by the authors.
\end{review}

\begin{response}
We have augmented Fig. $1$ by adding one zoom-in view for Arabidopsis plant.
Since bean dataset only includes one plant with good view, we do not provide a zoom-in view.
\end{response}

@@

% Reviewer 1: Q6
\begin{review}
Each of the databases mentioned in Table $1$ should be accompanied by a reference.
\end{review}

\begin{response}
We have the corresponding references in the prior work section, which follows the order as they appear in Table $2$.
To make it complete, we also added the reference to Table $2$.
\end{response}

% Reviewer 1: Q7
\begin{review}
The second paragraph of Sec. $2$ begins with ``we summarize all existing publicly available databases that are related to plant imagery".
This is a strong statement, particularly because other plant related image databases exist (e.g., ImageCLEF, ICL leaf database) which are omitted from the review.
The authors should adjust language and/or expand the literature review.
\end{review}

\begin{response}
We have adjusted the language by the statement of ``we summarize existing publicly available databases that are most related to our work".
\end{response}

@@

% Reviewer 1: Q8
\begin{review}
In the second paragraph in Sec. $2$, I believe the observation on single leaves imaged in a constrained environment does not apply to the dataset by (Haug and Ostermann, $2014$).
Please reformulate.
\end{review}

\begin{response}
It is correct that the dataset (Haug and Ostermann, $2014$) is not about single leaves imaged in a constrained environment.
We still category it in the first type because it does not include leaf segmentation.
All segmentation tasks are based on plant level.
We have reformulated this in the second paragraph in Sec. $2$.
\end{response}

% Reviewer 1: Q9
\begin{review}
It appears from Sec. $3.1$ that all plant subjects (respectively for Arabidopsis and bean) belong to the same genotype and that no treatments were performed.
This would entail that the proposed dataset cannot be used to investigate computer vision algorithms or imaging modalities in relation to group differences.
Could the authors comment on this?
\end{review}

\begin{response}
It is true that we do not compare group differences, based on morphology (for example).
However, we are using this database to address a fundamental issue with visual phenotyping: accurate and automated identification and tracking of individual leaves over developmental time scales (weeks).  
The reason this is important is highlighted in other sections, in particular in text we are adding to address Comment $2$ and $4$.  
The inherent challenge is that leaves change in size, position, and shape as they emerge and grow. 
Also they may overlap or be overlapped by other leaves.  
I think that new text we have added more clearly emphasizes leaf identification and tracking over time rather than developing methods/algorithms to define group differences. 
We have added one paragraph in Conclusion to better reflect this. 
\end{response}

@@

% Reviewer 1: Q10
\begin{review}
In Sec. $3.2.1$ the authors remark that light used for night image acquisition does not influence plant development. 
A reference should be included to support this statement.
\end{review}

\begin{response}
We have revised paragraph $2$ in Sec. $3.2.1$ and added $2$ references to support this statement. 
\end{response}

@@

% Reviewer 1: Q14
\begin{review}
The conclusions (Sec. $6$) should be expanded.
\end{review}

\begin{response}
\todo{will expand after everything finished}
\end{response}

% Reviewer 1: Q15
\begin{review}
The acronym "MSU-PID" should be clearly defined when it first appears in text (p. $2$, line $51$)
\end{review}

\begin{response}
Except in the Abstract, the "MSU-PID" first appears in paragraph $4$ of Sec $1$.
We have clearly defined it as short for Michigan State University Plant Image Database.
\end{response}

@@

\begin{response}
We use some training images with groundtruth plant segmentation masks to learn a threshold for binary segmentation.
The learnt threshold is then applied to both training images and testing images to generate the image mask.
We have added this statement to the paper.
\end{response}

\vspace{1em}
\noindent {\large\textsc{Reviewer~2}}\\
\begin{tabular*}{\textwidth}{c}
\hline
\end{tabular*}

% Reviewer 2: Q21
\begin{review}
The authors argue that the most closely related work is that of Scharr et al $2014$.
They identify as weaknesses that it i) uses only RGB images and ii) can be used for a few vision problems.
However, upon reading the Scharr paper it is clear that the authors of that work, do mention that they collect additional data to be used in tracking context and for other applications.
It is not clear if the authors here refer to what is available data from Scharr et al or what is described in the paper?
Furthermore, the data in Scharr et al appear to originate from different mutants and under different treatments, and also imaged with different cameras.
Since this work does use only wildtypes and single cultivars this distinction should be made.
Furthermore, once leaf labeling is available several secondary annotations can be derived so in some sense Table $1$ should be annotated accordingly.
Nevertheless, I recommend the authors for arranging information as in Table $1$.
\end{review}

\begin{response}
We refer to Scharr et al $2014$ that the Leaf Segmentation Challenge database only includes independent images without tracking context.
The reason we do not include mutants is that we assume any computer vision algorithms that work on wildtypes should also work well on mutants as they have similar structure.
\\ %\textcolor{red}{I do not understand what to be added to Table $1$.}
\todo{TBD: Dr. Chen, please add some sentences about mutants in bean data. I recall we plan to capture additional bean data sets that have different mutants. Am I right?}
\end{response}

@@

\begin{response}
Yes, the distance to the plant is roughly $620$mm.  
The image planes are plotted not at the plant location, but at a distance proportional to the focal length of each camera.  
We added dashed lines to the figure to make it clearer that these planes do not correspond to the plant depth, and updated the caption to better explain it.
\end{response}

% Reviewer 2: Q25
\begin{review}
On Table $3$ you list resolutions for the acquired image data.  
This image resolution is much lower than the LSC database of Scharr et al. 
This limitation should be mentioned.
\end{review}

\begin{response}
We added one paragraph in the end of Sec. $4.1$ to address the trade-off between image resolution and experiment throughput.
\end{response}

% Reviewer 2: Q26
\begin{review}
On manual annotation process, did you use an extra annotator or a supervisor?
\end{review}

\begin{response}
The released label is labeled by one annotator. 
However, we do use extra annotator to label several images and the annotation error between different annotators is evaluated. 
\todo{Results?}
\end{response}

% Reviewer 2: Q27
\begin{review}
Your annotation process is completely interactive.
Any way to ``save interaction" by interactive segmentation approaches?
I applaud your comment on the difficulty of merging super-pixel results, but I would add at least somewhere that easier ways to annotate will be beneficial.
\end{review}

@@

\begin{response}
Our annotation is not interactive.
It is totally based on user input without any computer feedback except for visualization.
Leaf label is implemented by clicking several points along the boundary of the leaf.
Tip label is implemented by clicking the outer and inner tip points respectively.
We did explore other options for labeling and found this simple naive way worked the best.
\end{response}

% Reviewer 2: Q28
\begin{review}
It is unclear if you release this annotation tool? 
If not, please do. 
It will be extremely useful for the community.
\end{review}

\begin{response}
We will release the labeling tool together with the database.
\end{response}

@@

% Reviewer 2: Q30
\begin{review}
Does the annotation $\_$hour$\_$YY$\_$label.png contain a label for each pixel or only for the boundaries?
If yes, then can you obtain single boundary definition in between overlapping leaves?
\end{review}

\begin{response}
The annotated image is an image the same size as the original image.
And each pixel is annotated with a number.
The same number represents the same leaf and $0$ represents the background.
For overlapping leaves, we can visualize the relative location and annotate accordingly.
\end{response}

% Reviewer 2: Q31
\begin{review}
Based on your annotations can you find which leaf occludes which?
\end{review}

\begin{response}
During annotation, we can observe which leaf occludes which and annotate the overlapping area to the leaf on top.
However, it is hard to estimate which leaf occludes which from the annotations.
\end{response}

@@

% Reviewer 2: Q32
\begin{review}
The authors test an algorithm (developed by them) on the fluorescence part of the data.
Granted this algorithm is presented elsewhere on the same data.
I was wondering if the authors can either a) use the same algorithm on one of the other modalities, and how it would perform (assuming ground truth labeling obtained via propagation)?
OR b) if they can apply another benchmark method even from the broad CV literature on one of the CV problems considered in another modality.
I think doing one of the two, time permitting, will greatly assist the paper.
\end{review}

\begin{response}
\todo{Xi: apply to RGB modality and evaluate the performance with transferred labels. Transferred label is needed!}
\end{response}

@@

% Reviewer 2: Q33
\begin{review}
I do not subscribe to the term dense for such low resolution depth cameras. 
In my book dense refers to high res depth maps. 
Maybe the authors can reconsider the use of the term.
\end{review}

\begin{response}
We agree and have removed the term ``dense" from the depth map image.
\end{response}

% Reviewer 2: Q34
\begin{review}
I am not sure the authors used the correct reference for Erblichkeit $1903$. 
I think Erblichkeit is part of the title. 
A google search reveals this: http://caliban.mpipz.mpg.de/johannsen/erblichkeit/
with the author being: Wilhelm Ludwig Johannsen.
Please check.
\end{review}

\begin{response}
It is right that Erblichkeit is part of the title and the author's name is Wilhelm Ludwig Johannsen.
We have corrected it. 
\end{response}

### 2015-07-22 datapaper_calibration.tex
xm's first edits
final edit
xi_edit paper

A planar checkerboard pattern was used to calibrate all three cameras to obtain both intrinsic and extrinsic parameters. While the grid pattern is not visible in the depth image, it is nevertheless observed in the reflected IR image whose pixels correspond to the depth pixels. This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a $2$-parameter radial distortion of each camera. In this process the poses of all three cameras are also calculated relative to the checkerboard. The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as in Figure~\ref{fig:CameraConfiguration}.

@@

The time of flight depth measurements can have significant noise, and it is useful to both model it and quantify it. Doing so can lead to strategies to reduce noise as well as providing guidance to algorithms that use the depth measurements. Our goal in this section is to provide a simple noise model that can predict the empirically observed depth noise on smooth, Lambertian surfaces, such as plant leafs.

The depth noise, $\varepsilon$, is modeled as the sum of an image dependent term, $\varepsilon_I$, and a sensor dependent term, $\varepsilon_S$:
\begin{equation}
\varepsilon = \varepsilon_I + \varepsilon_S\label{eq:epsilon}
\end{equation}
The term $\varepsilon_I$ is a random variable for each pixel with a value that varies between subsequent images taken from a fixed pose of a static scene.  On the other hand, $\varepsilon_S$ is a random variable for each pixel that models its depth offset, and its value only changes when the scene changes.  The variance of $\varepsilon_I$ is estimated for each pixel of a fixed scene observed over multiple images. In our experiments we observed a flat, uniform albedo surface perpendicular to the camera at a sequence of depths, and for each depth acquired 300 images. Object depth, $d$, has a large impact on $\varepsilon_I$. For constant depth, we observed that the primary factor affecting the variance is the pixel radius, $r$, from the image center. Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis. Based on these observations we model $\sigma_I(d,r)$, the standard deviation of $\varepsilon_I$, as a function of depth and pixel radius.  From our experiments we build up a lookup table for this as plotted in Figure~\ref{fig:Noise}.

\begin{table*}[t!]
\begin{center}
\caption{Summary of Arabidopsis and Bean databases.}
\label{tab:stat}
\begin{tabular}{c|c|c|c|c|c}
\hline
% after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
Plants & Subjects & Days & Images/Day & Total Images & Annotated Images \\
\hline
Arabidopsis & $16$ & $9$ & $16$ & $2304\times 4$ & $576\times 4$ \\
\hline
Bean & $5$ & $5$ & $14$ & $350\times 4$ & $175\times 4$ \\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}
\begin{center}
\caption{Plant image resolution of Arabidopsis and Bean databases.}
\label{tab:resolution}
\begin{tabular}{c|c|c|c|c}
\hline
% after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
Plants & Fluorescence & IR & RGB & Depth \\
\hline
Arabidopsis & $\sim$$240\times240$ & $\sim$$240\times240$ & $\sim$$120\times120$ & $\sim$$25\times25$ \\
%\hline
Bean & $1000\times640$ & $1000\times640$ & $380\times720$ & $90\times190$ \\
\hline
\end{tabular}
\end{center}
\end{table*}

Averaging over repeated images of a scene will not remove all the depth error as there are pixel depth offsets that are constant for images of the same scene. We model these with $\varepsilon_S$. To estimate its standard deviation, $\sigma_S$, we first average over many depth measurement images, in our case 300, to obtain pixel depth estimates that approximately eliminate the effect of $\varepsilon_I$. Then by calculating true ray depths on a known surface, in our case the observed plane, and further assuming that $\varepsilon_S$ has the same standard deviation for all pixels, $\sigma_S$ is obtained as the standard deviation of the error between averaged depths and known depths. In our experiments we obtained $\sigma_S=6.5mm$, and found that it was insensitive to changes in depth.

>>>>

A planar checkerboard pattern was used to calibrate all three cameras to obtain both intrinsic and extrinsic parameters. 
While the grid pattern is not visible in the depth image, it is nevertheless observed in the reflected IR image whose pixels correspond to the depth pixels. 
This enables the use of Zhang's method~\cite{Zhang2000} to calculate the intrinsic parameters including a $2$-parameter radial distortion of each camera. 
In this process the poses of all three cameras are also calculated relative to the checkerboard. 
The intrinsic and extrinsic parameters are stored as text files, and a Matlab function is provided that reads the parameters and can plot the camera poses as in Fig.~\ref{fig:CameraConfiguration}.

@@

The time of flight depth measurements can have significant noise, and it is useful to both model it and quantify it. 
Doing so can lead to strategies to reduce noise as well as providing guidance to algorithms that use the depth measurements. 
Our goal in this section is to provide a simple noise model that can predict the empirically observed depth noise on smooth, Lambertian surfaces, such as plant leaves.

The depth noise $\varepsilon$ is modeled as the sum of an image dependent term $\varepsilon_I$ and a sensor dependent term $\varepsilon_S$:
\begin{equation}
\varepsilon = \varepsilon_I + \varepsilon_S. \label{eq:epsilon}
\end{equation}
The term $\varepsilon_I$ is a random variable for each pixel with a value that varies between subsequent images taken from a fixed pose of a static scene.  
On the other hand, $\varepsilon_S$ is a random variable for each pixel that models its depth offset, and its value only changes when the scene changes.  
The variance of $\varepsilon_I$ is estimated for each pixel of a fixed scene observed over multiple images. 
In our experiments we observed a flat, uniform albedo surface perpendicular to the camera at a sequence of depths, and for each depth acquired $300$ images. 
Object depth, $d$, has a large impact on $\varepsilon_I$. 
For constant depth, we observed that the primary factor affecting the variance is the pixel radius $r$, from the image center. 
Physically we expect this dependence is due to a circularly symmetric illuminating beam closely aligned with the optical axis. 
Based on these observations we model $\sigma_I(d,r)$, the standard deviation of $\varepsilon_I$, as a function of depth and pixel radius.  
From our experiments we build up a lookup table for this as plotted in Fig.~\ref{fig:Noise}.

\begin{table*}[t!]
\begin{center}
\caption{Summary of Arabidopsis and Bean databases.\todo{last column needs to be updated}}
\label{tab:stat}
\begin{tabular}{c|c|c|c|c|c}
\hline
% after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
Plants & Subjects & Days & Images/Day & Total Images & Annotated Images \\
\hline
Arabidopsis & $16$ & $9$ & $16$ & $2304\times 4$ & $576\times 4$ \\
\hline
Bean & $5$ & $5$ & $14$ & $350\times 4$ & $175\times 4$ \\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}
\begin{center}
\caption{Plant image resolution of Arabidopsis and Bean databases, computed based on the yellow ROIs in Fig.~\ref{fig:fourmodality}.}
\label{tab:resolution}
\begin{tabular}{c|c|c|c|c}
\hline
% after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
Plants & fluorescence & IR & RGB & depth \\
\hline
Arabidopsis & $\sim$$240\times240$ & $\sim$$240\times240$ & $\sim$$120\times120$ & $\sim$$25\times25$ \\
%\hline
Bean & $1000\times640$ & $1000\times640$ & $380\times720$ & $90\times190$ \\
\hline
\end{tabular}
\end{center}
\end{table*}

Averaging over repeated images of a scene will not remove all the depth error as there are pixel depth offsets that are constant for images of the same scene. 
We model these with $\varepsilon_S$. 
To estimate its standard deviation $\sigma_S$, we first average over many depth measurement images, in our case $300$, to obtain pixel depth estimates that approximately eliminate the effect of $\varepsilon_I$. Then by calculating true ray depths on a known surface, in our case the observed plane, and further assuming that $\varepsilon_S$ has the same standard deviation for all pixels, $\sigma_S$ is obtained as the standard deviation of the error between averaged depths and known depths. In our experiments we obtained $\sigma_S=6.5mm$ and found that it was insensitive to changes in depth.

### 2015-07-22 datapaper_intro.tex
xi_edit paper

With the rapid growth of world population and the loss of arable land, there is an increasing desire to improve the yield and quality of crops, where the understanding of the genetic mechanisms to influence plant growth is a key enabler~\cite{doos2002population}.
%
A classic genetics approach is to produce a diverse population of mutant lines, grow them either in growth chambers with simulated environmental conditions or directly in the field, visually observe the plants during the growth period, and finally identify plant morphological or physiological patterns that tightly associate with key growth factors~\cite{houle2010phenomics}.
%
While many factors can be assessed quantitatively, which is essential for high-throughput study, one of the bottleneck in this research pipeline is plant visual phenotyping~\cite{walter2015plant}.

@@

Plants develop through a complex interaction between genotype and environment. This determines their structure and functions and thus performance such as yield or efficient use of resources. In order to understand the genetic basis of these economically important parameters, it is essential to quantitatively assess plant phenotypes and then identify the latent relationships to genotypes and environmental factors.
%
Plant visual phenotyping has been performed by farmers and breeders for more than 5,000 years. In the past, traditional phenotyping is based on experience and intuition, and is laborious~\cite{johannsenerblichkeit}. Recent progresses in imaging sensor, robotics and automation technologies lead to the development of the ever-increasing new field of highly automated, non-destructive {\it plant visual phenotyping}~\cite{furbank2011phenomics,cruz2015depi}. %Modern plant phenotyping is a comprehensive, large-scale assessment of plant traits such as growth, development, tolerance, resistance, architecture, physiology, ecology, yield, and metadata that form the basis for more complex parameters.
%
The objective of modern  plant visual phenotyping is to analyze and categorize the morphological  characteristics of plants, thus accurately quantifying plant traits. %It advances crop yield improvement and enables the systematic study of the environmental plasticity of plants. %
In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve problems related to growth, development, stress tolerance, resistance, and so on.
%
%In old days, plant phenotyping was conducted through manual visual observation~\cite{Erblichkeit1903}. Today, motivated by the increasing lower cost and increasing diversity of imaging sensors technologies, image-based automatic plant visual phenotyping is quickly growing into a desirable and viable solution~\cite{furbank2011phenomics,cruz2015depi}.
%
A key advance in visual phenotyping is the capability to non-invasively capture plant traits, enabling continuous measurements that are necessary to monitor plants during growth and/or under stress conditions. Vision based phenotyping also increases the throughput of phenotyping experiments by eliminating destructive operations. The increased capacity allows more genotypes or biological replicates to be examined under the same environmental conditions~\cite{fahlgren2015lights,walter2015plant}.

One practical goal of plant visual phenotyping is to accurately quantify plant traits, particularly those related to photosynthetic performance, growth, yield and resilience to environmental stress.  For the approach to be of practical use, plants must be monitored continuously, over developmental time scales and under conditions that more closely approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
%
The capacity to identify and track individual leaves throughout experiments will be important for more clearly defining phenotypic behaviors related to leaf specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress. For example, decreases in the average photosynthetic efficiency ($\Phi_{II}$, quantum yield of photochemistry at photosystem II) of an Arabidopsis plant may reflect a heterogeneous distribution of $\Phi_{II}$ values across its entire photosynthetic surface area~\cite{oxborough2004imaging}. In this case, mapping distributions to individual leaves can be used to distinguish between a systemic (whole plant) effect and localization of the effect to subset leaves.
%
In addition, using more detailed information, such as leaf angle and height/position as well as canopy density/size, it should be possible to improve estimates of total photosynthetic capacity over time (particularly for plants with more complex canopies, like common bean or tobacco), since these factors influence absorption and availability of the light energy used to drive photosynthesis.

@@

To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality Plant Imagery Database through an interdisciplinary effort at Michigan State University (MSU), termed ``MSU-PID''.
As illustrated in Figure~\ref{fig:fourmodality}, the MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of imaging sensors, i.e., fluorescence, infrared (IR), RGB color, and depth.
All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days.
Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities.

%
The type and amount of manual labels on a database is a critical enabler to the potential applications of the database.
For a subset of the MSU-PID database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips and leaf segments.
As a result, MSU-PID is suitable for a number of applications, including 1) {\it leaf segmentation} that aims at estimating the correct segmentation mask of each leaf in an image, 2) {\it leaf counting} that estimates the correct number of leaves within a plant, 3) {\it leaf alignment} that aligns the two tips of each leaf -- the cornerstone of the leaf structure, and 4) {\it leaf tracking} that is designed to track each leaf over time.
Finally, to provide a performance baseline for future research and comparison, we apply our automatic leaf segmentation framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the unique challenge of image analysis on this database.

In summary, this paper and our database have made the following main contributions.
\begin{itemize}
\item MSU-PID is the first {\it multi-modality} plant image database. This allows researchers to study the strength and weakness of individual modality, as well as their various combinations in plant image analysis.
\item Our unique imaging setup and the variety of manual labels make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis applications, including leaf segmentation, leaf counting, leaf alignment, leaf tracking, and potentially leaf growth prediction and $3$D leaf reconstruction.
\end{itemize}

>>>>

With the rapid growth of world population and the loss of arable land, there is an increasing desire to improve the yield and quality of crops, where the understanding of the genetic mechanisms to influence plant growth is a key enabler~\cite{doos2002population}.
%
A classic genetic approach is to produce a diverse population of mutant lines, grow them either in growth chambers with simulated environmental conditions or directly in the field, visually observe the plants during the growth period, and finally identify plant morphological or physiological patterns that tightly associate with key growth factors~\cite{houle2010phenomics}.
%
While many factors can be assessed quantitatively, which is essential for high-throughput study, one of the bottleneck in this research pipeline is plant visual phenotyping~\cite{walter2015plant}.

@@

Plants develop through a complex interaction between genotype and environment. 
This determines their structure, functions, and thus performance such as yield or efficient use of resources. 
In order to understand the genetic basis of these economically important parameters, it is essential to quantitatively assess plant phenotypes and then identify the latent relationships to genotypes and environmental factors.
%
Plant visual phenotyping has been performed by farmers and breeders for more than $5,000$ years. 
In the past, traditional phenotyping is based on experience and intuition, and is laborious~\cite{johannsenerblichkeit}. 
Recent progresses in imaging sensor, robotics and automation technologies lead to the development of the ever-increasing new field of highly automated, non-destructive {\it plant visual phenotyping}~\cite{furbank2011phenomics,cruz2015depi}. 
%Modern plant phenotyping is a comprehensive, large-scale assessment of plant traits such as growth, development, tolerance, resistance, architecture, physiology, ecology, yield, and metadata that form the basis for more complex parameters.
%
The objective of modern  plant visual phenotyping is to analyze and categorize the morphological characteristics of plants, and thus accurately quantifying plant traits. %It advances crop yield improvement and enables the systematic study of the environmental plasticity of plants. %
In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the purpose of raising testable biological hypotheses to solve problems related to growth, development, stress tolerance, resistance, and so on.
%
%In old days, plant phenotyping was conducted through manual visual observation~\cite{Erblichkeit1903}. Today, motivated by the increasing lower cost and increasing diversity of imaging sensors technologies, image-based automatic plant visual phenotyping is quickly growing into a desirable and viable solution~\cite{furbank2011phenomics,cruz2015depi}.
%
A key advance in visual phenotyping is the capability to non-invasively capture plant traits, enabling continuous measurements that are necessary to monitor plants during growth and/or under stress conditions. Vision based phenotyping also increases the throughput of phenotyping experiments by eliminating destructive operations. 
The increased capacity allows more genotypes or biological replicates to be examined under the same environmental conditions~\cite{fahlgren2015lights,walter2015plant}.

One practical goal of plant visual phenotyping is to accurately quantify plant traits, particularly those related to photosynthetic performance, growth, yield and resilience to environmental stress.  
For the approaches to be of practical use, plants must be monitored continuously, over developmental time scales and under conditions that more closely approximate the native environment (dynamic 'field' conditions)~\cite{fahlgren2015lights,walter2015plant}.
%
The capacity to identify and track individual leaves throughout experiments is important for more clearly defining phenotypic behaviors related to leaf specific factors such as developmental age~\cite{schottler2015photosynthetic} and/or following the application of stress. 
For example, decrease in the average photosynthetic efficiency ($\Phi_{II}$, quantum yield of photochemistry at photosystem II) of an Arabidopsis plant may reflect a heterogeneous distribution of $\Phi_{II}$ values across its entire photosynthetic surface area~\cite{oxborough2004imaging}. 
In this case, mapping distributions to individual leaves can be used to distinguish between a systemic (whole plant) effect and localization of the effect to subset leaves.
%
In addition, using more detailed information, such as leaf angle and height/position as well as canopy density/size, it should be possible to improve estimation of total photosynthetic capacity over time (particularly for plants with more complex canopies, like common bean or tobacco), since these factors influence absorption and availability of the light energy used to drive photosynthesis.

@@

To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality Plant Imagery Database through an interdisciplinary effort at Michigan State University (MSU), which is termed ``MSU-PID''.
As illustrated in Fig.~\ref{fig:fourmodality}, the MSU-PID database includes the imagery of two types of plants (Arabidopsis and bean, both are widely used in plant research) captured by four types of imaging sensors, i.e., fluorescence, infrared (IR), RGB color, and depth.
All four sensors are synchronized and are programmed to periodically capture imagery data for multiple consecutive days.
Checkerboard-based camera calibration is performed between a pair of sensors, which results in the explicit correspondence between the pixels of {\it any} two modalities.
\todo{Need to be updated about the transformation}

The type and amount of manual labels on a database is a critical enabler to the potential applications of the database.
For a subset of the MSU-PID database, we manually label the ground truth regarding the leaf identification number, locations of leaf tips, and leaf segments.
As a result, MSU-PID is suitable for a number of applications, including 1) {\it leaf segmentation} that aims at estimating the correct segmentation mask of each leaf in an image, 2) {\it leaf counting} that estimates the correct number of leaves within a plant, 3) {\it leaf alignment} that aligns the two tips of each leaf -- the cornerstone of the leaf structure, and 4) {\it leaf tracking} that is designed to track each leaf over time.
Finally, to provide a performance baseline for future research and comparison, we apply our automatic leaf segmentation framework~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the unique challenge of image analysis on this database.

In summary, this paper and our database have made the following main contributions.
\begin{itemize}
\item MSU-PID is the first {\it multi-modality} plant image database. This allows researchers to study the strength and weakness of individual modality, as well as their various combinations in plant image analysis.
\item Our unique imaging setup and the variety of manual labels make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis applications including leaf segmentation, leaf counting, leaf alignment, leaf tracking, and potentially leaf growth prediction and $3$D leaf reconstruction.
\end{itemize}

### 2015-07-22 datapaper_plants.tex
xi_edit paper

\section{Data Collection}\label{sec:2}

@@

{\it Arabidopsis thaliana} (ecotype Col-0) plants were grown at $20^{\circ}C$, under a $16$ hr:$8$ hr day night cycle with a daylight intensity set at $100~\mu mol~photons~m^{-2} s^{-1}$.
%
Black bean plants ({\it Phaseolus vulgaris L.}) of the cultivar Jaguar, were grown under a $14$ hr:$10$ hr day night cycle with night and day temperatures of $18^{\circ}C$ and $24^{\circ}C$ respectively, and a daylight intensity set at $200~\mu mol~photons~m^{-2} s^{-1}$.
%
Note that the bean plants were watered with half-strength Hoaglands solution three times per week.

In all cases, seeds were planted in soil covered with a black foam mask in order to minimize the fluorescence background from algal growth.
%
Two-week-old plants ({\it Arabidopsis} or bean) were transferred to imaging chambers and allowed to acclimate for $24$ hours to the LED lighting before the start of the data collection. 
Growth conditions as described above were maintained for each set of plants for the duration of image collection.

>>>>

\section{Data Collection}
\label{sec:2}

@@

{\it Arabidopsis thaliana} (ecotype Col-0) plants were grown at $20^{\circ}C$, under a $16$hr : $8$hr day-night cycle with a daylight intensity set at $100~\mu mol~photons~m^{-2} s^{-1}$.
%
Black bean plants ({\it Phaseolus vulgaris L.}) of the cultivar Jaguar, were grown under a $14$hr : $10$hr day-night cycle with day and night temperatures of $24^{\circ}C$ and $18^{\circ}C$ respectively, and a daylight intensity set at $200~\mu mol~photons~m^{-2} s^{-1}$.
%
Note that the bean plants were watered with half-strength Hoaglands solution three times per week.

In all cases, seeds were planted in soil covered with a black foam mask in order to minimize the fluorescence background from algal growth.
%
Two-week-old plants ({\it Arabidopsis} and bean) were transferred to imaging chambers and allowed to acclimate for $24$ hours to the LED lighting before the start of the data collection.
Growth conditions as described above were maintained for each set of plants for the duration of image collection.
